
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
```

# railroadR

> Railroad Diagrams for R

[![Linux Build Status](https://travis-ci.org//railroadR.svg?branch=master)](https://travis-ci.org//railroadR)
[![](http://www.r-pkg.org/badges/version/railroadR)](http://www.r-pkg.org/pkg/railroadR)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/railroadR)](http://www.r-pkg.org/pkg/railroadR)


Generate railroad diagrams in R with the convenience and infrastructure of htmlwidgets, or eventually create static SVG railroad diagrams for use in non-htmlwidget situations. Thanks so much to Tab Atkins, Jr. for the JavaScript library [railroad-diagrams](https://github.com/tabatkins/railroad-diagrams) that actually does all the hard work.

## Installation

```{r eval = FALSE}
devtools::install_github("timelyportfolio/railroadR")
```

## Usage

```{r eval = FALSE}
library(railroadR)

railroad(
  Choice(0, 'u', 'U'),
	Choice(0, 'r', 'R'),
	Choice(0, 'l', 'L'),
	'(',
	Choice(1,
		Optional(NonTerminal('WS')),
		Sequence(
			Optional(NonTerminal('WS')),
			NonTerminal('STRING', '#string'),
			Optional(NonTerminal('WS'))),
		Sequence(
			Optional(NonTerminal('WS')),
			OneOrMore(
				Choice(0,
					NonTerminal('not " \' ( ) WS or NPC'),
          NonTerminal('escape'))),
          Optional(NonTerminal('WS'))
		    )
		),
  ')'
)
```

## License

MIT + file LICENSE © [Kenton Russell](https://github.com/timelyportfolio/railroadR).

railroad-diagrams JavaScript library [CC0](http://creativecommons.org/publicdomain/zero/1.0/) LICENSE © [Tab Atkins, Jr.](https://github.com/tabatkins/railroad-diagrams)
